True versus apparent shapes of astrophysical bow shocks

### 2017-02-07 papers/Paper1/sec-thin-shell.tex
Final hand-improvements to Fig 5
Add figure of residuals to head-tail fits

@@

\begin{figure*}
  \centering
  \includegraphics[height=0.85\textheight]{figs/conic-head-tail-analytic}
  \caption{Double quadric fits to thin shell
    solutions.}
  \label{fig:head-tail}
\end{figure*}

>>>>

In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with

We therefore 
We carry out three-level nested fits to determine the

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
  \caption{Double quadric fits to thin shell
    solutions.}
  \label{fig:head-tail}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
  \caption[]{Residuals of double quadric fits to thin shell solutions.
    Residuals are expressed as the fractional error in the
    complementary angle \(\theta_1\) for the same parameters as are shown
    in Fig.~\ref{fig:head-tail}.}
  \label{fig:head-tail-residuals}
\end{figure*}
